---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PLindleyROC

<!-- badges: start -->
[![R-CMD-check](https://github.com/ErtanSU/PLindleyROC/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ErtanSU/PLindleyROC/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/ErtanSU/PLindleyROC/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ErtanSU/PLindleyROC)
<!-- badges: end -->

The goal of PLindleyROC is to evaluate the Receiver Operating Characteristic (ROC) for Power Lindley Distribution. Additionally, The performace asssesments can be performed associated with the Bi-Power Lindley ROC model.

## Installation

You can install the development version of PLindleyROC via the following code:

``` r
# install.packages("devtools")
devtools::install_github("ErtanSU/PLindleyROC")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(PLindleyROC)
dPLD(c(1,2,3,4,5,200),alpha=3,beta=2)
```

```{r}
library(PLindleyROC)
pPLD(c(.5,1,2,3,4),alpha=3,beta=2)
```

```{r}
library(PLindleyROC)
qPLD(c(.9971,0.5,0.3),alpha=3,beta=2)
```

```{r}
library(PLindleyROC)
rPLD(10,alpha=3,beta=2)
```

```{r}
library(PLindleyROC)
plAUC(alpha1=2,beta1=5,alpha2=6,beta2=1)
```

```{r}
library(PLindleyROC)
plJ(alpha1=2,beta1=5,alpha2=6,beta2=1,init=0)
```

```{r}
library(PLindleyROC)
plER(alpha1=2,beta1=5,alpha2=6,beta2=1,init=0)
```

```{r}
library(PLindleyROC)
plCZ(alpha1=2,beta1=5,alpha2=6,beta2=1,init=0)
```

```{r}
library(PLindleyROC)
plIU(alpha1=2,beta1=5,alpha2=6,beta2=1,init=0)
```

```{r}
library(PLindleyROC)
plNI(alpha1=2,beta1=5,alpha2=6,beta2=1,init=0.5)
```

```{r pressure, echo = TRUE}
library(PLindleyROC)
x=c(1,2,3,4)
y=c(2,3,4)
plROC(x,y,alpha1=2,beta1=5,alpha2=6,beta2=1,empirical=FALSE)
```

```{r}
library(PLindleyROC)
prfROC(ctp=0.5,alpha1=2,beta1=5,alpha2=6,beta2=1)
```

## Corresponding Author

Department of Statistics, Faculty of Science, Selcuk University, 42250, Konya, Turkey  <br />

Email:https://www.researchgate.net/profile/Ertan-Akgenc

## References

Attwood, K., Hou, S., and Hutson, A., 2022,
*Application of the skew exponential power distribution to ROC curves*, Journal of Applied Statistics, 1-16.

Ghitany M., Al-Mutairi D. K., Balakrishnan N., and Al-Enezi L., 2013,
*Power lindley distribution and associated inference*, Computational Statistics & Data Analysis, 64,20–33.

 Liu, X., 2012,
*Classification accuracy and cut point selection*, Statistics in medicine, 31(23), 2676-2686.

Nahm, F. S., 2022,
*Receiver operating characteristic curve: overview and practical use for clinicians*, Korean journal of anesthesiology, 75(1), 25-36.

Perkins, N. J., and Schisterman, E. F., 2006,
*The inconsistency of “optimal” cutpoints obtained using two criteria based on the receiver operating characteristic curve*, American journal of epidemiology, 163(7), 670-675.

Pundir, S. and Amala, R., 2014,
*Evaluation of area under the constant shape bi-weibull roc curve*, Journal of Modern Applied Statistical Methods, 13(1),1-20.

Youden, W. J., 1950,
*Index for rating diagnostic tests*, Cancer, 3(1), 32-35.

